Reproducible Workflow on a Public Cloud for Computational Fluid Dynamics

### 2019-03-23 tex/MesnardoBarba2019.tex
Add sentences in intro about terminologies

>>>>

Reproducible research and replication studies are essential components for the progress of evidence-based science, even more since science today advances via computation.
More than ever we use computer simulations to create new knowledge.
But how do we certify that this new knowledge is justified, that there is enough evidence to support it?
With constant increase in the rate of submissions to journals as well as software and data getting more complex, it becomes difficult to verify and corroborate what computational scientists present in journal and conferences \cite{donoho_et_al_2009}.

The literature is often swamped with confused, and sometimes contradictory, meanings for reproducible research, reproducibility, replicability, repetition, and so on \cite{barba_2018}.
It is thus worth clarifying these terms.
The term ``reproducible research'' in reference to computational studies that can be reproduced by other scientists was introduced by geophysics professor Jon Claerbout in the 1990s. He and his research group at Stanford created a reproducible-research environment\cite{schwab_et_al_2000} in which, the goal was complete documentation of scientific computations, in such way that a reader could reproduce all the results and figures in a paper using the author-provided computer programs and raw data.
This ability requires open data and open source software and, for this reason, the reproducibility movement is closely linked with the open science movement.
In subsequent years, the term ``replication'' was distinctly adopted to refer to an independent study that rerun experiments to generate new data which, when analyzed, lead to the same findings.
We follow this convention, clarified more recently in a report from the National Academies of Sciences, Engineering, and Medicine.
